### 2025-02-11 player-evaluation.qmd
20250210 - embrace the chaos

>>>>

However, another perspective is to embrace the chaos and uncertainty that is part of fantasy football; one is better positioned to win a given week if you have one or a few players that "go off"—i.e., that score lots of points.
Thus, starting boom-or-bust players can make it more likely that you win in the "boom weeks"; however, this may also mean having some "bust weeks".
